MCC Prior Overview

### 2018-05-10 stats/mcc_priors_overview.Rmd
adding noisy model predictions and weaker priors
add weaker prior dis-preference

```{r data}
d1 <- read_csv(file="novel.weak.data2.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "2_medium")

x <- d1 %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(n = length(correct)) %>%
  filter(n > 2)

d1 <- d1 %>%
  filter(!id %in% x$id)

d2 <- read_csv(file="novel.weak.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "1_weak")

d3 <- read_csv(file="novel.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "3_strong")

d4 <-read_csv(file="pref.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "3_strong")

@@

d <- bind_rows(d1,d2,d3,d4,d5)
```

>>>>

```{r data}
d3 <- read_csv(file="novel.weak.data2.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "2_medium")

d4 <- read_csv(file="novel.weak.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "1_weak")

d1 <- read_csv(file="novel.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "3_strong")

d2 <-read_csv(file="pref.data.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "3_strong")

@@

d6 <-read_csv(file="pref.weak.data3.csv") %>%
  mutate(trial_type = ifelse(trial == "train", "train", "test"),
         strength = "1_weak")

d <- bind_rows(d1,d2,d3,d4,d5,d6)

# check if someone got both training trials wrong
d %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(sum = sum(correct)) %>%
  filter(sum == 0)

# check if someone did multiple experiments
# yes, six people
d %>%
  filter(trial_type == "train") %>%
  group_by(id)%>%
  summarise(n = length(correct)) %>%
  filter(n > 2)

# exclude those who did both experiments
# keep first time they participated

d <- d %>% 
  distinct(id, alltrial, .keep_all = TRUE)
```
